Twists of supersymmetric gauge theories

### 2019-08-06 paper.tex
Started some notes on 9d, also some minor rearrangements and comments

\tikzstyle{s16} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black,fill=red!30]
\tikzstyle{s16chiral} = [s16, dashed]
\tikzstyle{s8} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black,fill=orange!30]
\tikzstyle{s4} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black,fill=yellow!30]
\tikzstyle{s2chiral} = [rectangle, dashed, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black,fill=green!30]
\tikzstyle{dimension} = [ellipse, text centered, text width=1cm, minimum height=1cm, draw=black]
\tikzstyle{arrow} = [thick,->,>=stealth]

@@

\begin{dfn}
Let $X,Y$ be complex manifolds and $M$ a smooth manifold.
Let $\fg$ be an $L_\infty$ algebra which is finite dimensional in each cohomological degree. 
The {\bf mixed holomorphic-Dolbeault-topological BRST theory} \brian{blah, terrible name} on $X \times Y \times M$ is the local $L_\infty$ algebra defined by
\[
\cF[-1] = \Omega^{0,\bu}_X \Hat{\otimes} \Omega^{\bu,\bu}_Y \Hat{\otimes} \Omega^\bu_M \otimes \fg .
\] 
The $L_\infty$ structure is the one induced from $\fg$ together with the dg commutative product on differential forms. 
This is a classical BRST theory by choosing $Q_{BRST} = 0$ and $I_{BRST} = 0$. 
In other words, $\cF$ is defined by the mapping stack
\[
{\rm Map} (X_{\dbar} \times Y_{\rm Dol} \times M_{\rm dR}, B \fg) .
\]

@@

@@

\begin{theorem}
The holomorphic twist of 10d super Yang-Mills theory on a Calabi-Yau 5-fold $X$ is equivalent to holomorphic Chern-Simons theory on $X$.
\end{theorem}

@@

\subsection{Dimension 9}

% \cN=1 SYM

@@

% \cN=1 SYM

@@

% \cN=1 SYM

@@

% \cN=(1, 1) SYM

% \cN=(1, 0) SYM with matter in a pseudo-real representation. Construct the L_infinity action of supersymmetry

@@

% \cN=2 SYM
% \cN=1 SYM with matter in a pseudo-real representation.

@@

\begin{landscape}
\begin{figure}
\begin{tikzpicture}[node distance=0.5cm and 0.5cm, text width=2cm]
\node (101) [s16chiral] {Rank $(1, 0)$. $d=5$};
\node (91) [s16, below=of 101] {Rank $1$. $d=5$};
\node (82) [s16, below=of 91] {Rank $(1, 1)$. $d=5$};
\node (81) [s16, left=of 82] {Rank $(1, 0)$. $d=4$};
\node (825) [right=of 82] {};
\node (83) [s16, right=of 825] {Rank $(1, 0)$. $d=8$};
\node (71) [s16, below=of 81] {Rank $1$. $d=4$};
\node (72) [s16, below=of 82] {Rank $2$. $d=5$};
\node (73) [s16, below=of 83] {Rank $1$. $d=7$};
\node (62) [s16, below=of 71] {Rank $(1, 1)$. $d=4$};
\node (61) [s8, left=of 62] {Rank $(1, 0)$. $d=3$};
\node (63) [s16, below=of 72] {Rank $(2, 2)$. $d=5$};
\node (64) [s16chiral, right=of 63] {Rank $(2, 0)$. $d=5$};
\node (65) [s16, below=of 73, right=of 64] {Rank $(1, 1)$. $d=6$};
\node (51) [s8, below=of 61] {Rank $1$. $d=3$};
\node (52) [s16, below=of 62] {Rank $2$. $d=4$};
\node (53) [s16, below=of 63] {Rank $4$. $d=5$};
\node (54) [s16, below=of 64] {Rank $2$. $d=5$};
\node (42) [s8, below=of 51] {Rank $(1, 1)$. $d=3$};
\node (41) [s4, left=of 42] {Rank $(1, 0)$. $d=2$};
\node (43) [s16, right=of 42] {Rank $(2, 2)$. $d=4$};
\node (44) [s16, right=of 43] {Rank $(2, 1)$. $d=4$};
\node (45) [s8, right=of 44] {Rank $(2, 0)$. $d=4$};
\node (31) [s4, below=of 41] {Rank $1$. $d=2$};
\node (32) [s8, below=of 42] {Rank $2$. $d=3$};
\node (22) [s4, below=of 31] {Rank $(1, 1)$. $d=2$};
\node (21) [s2chiral, left=of 22] {Rank $(1, 0)$. $d=1$};

\node (2d) [dimension, left=of 21] {2d};
\node (3d) [dimension, above=of 2d] {3d};
\node (4d) [dimension, above=of 3d] {4d};
\node (5d) [dimension, above=of 4d] {5d};
\node (6d) [dimension, above=of 5d] {6d};
\node (7d) [dimension, above=of 6d] {7d};
\node (8d) [dimension, above=of 7d] {8d};
\node (9d) [dimension, above=of 8d] {9d};
\node (10d) [dimension, above=of 9d] {10d};
\end{tikzpicture}
\caption{Orbits of square-zero supercharges.}
\label{fig:superchargeorbits}
\end{figure}
\end{landscape}

>>>>

\tikzstyle{s16} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=red!30]
\tikzstyle{s16chiral} = [s16, dashed]
\tikzstyle{s8} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=orange!30]
\tikzstyle{s4} = [rectangle, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=yellow!30]
\tikzstyle{s2chiral} = [rectangle, dashed, rounded corners, minimum width=1.8cm, minimum height=1cm,text centered, draw=black,fill=green!30]
\tikzstyle{dimension} = [circle, text centered, text width=0.7cm, minimum height=0.7cm, draw=black]
\tikzstyle{arrow} = [thick,->,>=stealth]

@@

\begin{dfn}
Let $X,Y$ be complex manifolds and $M$ a smooth manifold.
Let $\fg$ be an $L_\infty$ algebra which is finite dimensional in each cohomological degree. 
The {\bf mixed holomorphic-Dolbeault-topological BRST theory} \brian{blah, terrible name} \chris{I don't really understand why this thing needs a name, since it's only a theory in a trivial way, with zero action.  Why not just call this thing $\cF$, call its shifted cotangent something like ``generalized BF theory'', then if $\fg$ has a pairing call the theory built out of $\cF$ with its AKSZ structure something like ``generalized Chern-Simons theory'' (I'm brainstorming other names too: e.g. ``Hodge-Chern-Simons theory'')?  Or do you want to reserve the name Chern-Simons for the case where $\fg$ is a Lie algebra, not an $L_\infty$ algebra?} on $X \times Y \times M$ is the local $L_\infty$ algebra defined by
\[
\cF[-1] = \Omega^{0,\bu}_X \Hat{\otimes} \Omega^{\bu,\bu}_Y \Hat{\otimes} \Omega^\bu_M \otimes \fg .
\] 
The $L_\infty$ structure is the one induced from $\fg$ together with the dg commutative product on differential forms. 
This is a classical BRST theory by choosing $Q_{BRST} = 0$ and $I_{BRST} = 0$. 
In other words, $\cF$ is defined by the mapping stack
\[
{\rm Map} (X_{\dbar} \times Y_{\rm Dol} \times M_{\rm dR}, B \fg) .
\]

@@

%\begin{landscape}
\begin{figure}
\begin{tikzpicture}[node distance=0.35cm and 0.35cm, text width=1.8cm]
\node (101) [s16chiral] {Rank $(1, 0)$ $d=5$};
\node (91) [s16, below=of 101] {Rank $1$ $d=5$};
\node (82) [s16, below=of 91] {Rank $(1, 1)$ $d=5$};
\node (81) [s16, left=of 82] {Rank $(1, 0)$ $d=4$};
\node (825) [right=of 82] {};
\node (83) [s16, right=of 825] {Rank $(1, 0)$ $d=8$};
\node (71) [s16, below=of 81] {Rank $1$ $d=4$};
\node (72) [s16, below=of 82] {Rank $2$ $d=5$};
\node (73) [s16, below=of 83] {Rank $1$ $d=7$};
\node (62) [s16, below=of 71] {Rank $(1, 1)$ $d=4$};
\node (61) [s8, left=of 62] {Rank $(1, 0)$ $d=3$};
\node (63) [s16, below=of 72] {Rank $(2, 2)$ $d=5$};
\node (64) [s16chiral, right=of 63] {Rank $(2, 0)$ $d=5$};
\node (65) [s16, below=of 73, right=of 64] {Rank $(1, 1)$ $d=6$};
\node (51) [s8, below=of 61] {Rank $1$ $d=3$};
\node (52) [s16, below=of 62] {Rank $2$ $d=4$};
\node (53) [s16, below=of 63] {Rank $4$ $d=5$};
\node (54) [s16, below=of 64] {Rank $2$ $d=5$};
\node (42) [s8, below=of 51] {Rank $(1, 1)$ $d=3$};
\node (41) [s4, left=of 42] {Rank $(1, 0)$ $d=2$};
\node (43) [s16, right=of 42] {Rank $(2, 2)$ $d=4$};
\node (44) [s16, right=of 43] {Rank $(2, 1)$ $d=4$};
\node (45) [s8, right=of 44] {Rank $(2, 0)$ $d=4$};
\node (31) [s4, below=of 41] {Rank $1$ $d=2$};
\node (32) [s8, below=of 42] {Rank $2$ $d=3$};
\node (22) [s4, below=of 31] {Rank $(1, 1)$ $d=2$};
\node (21) [s2chiral, left=of 22] {Rank $(1, 0)$ $d=1$};

\node (2d) [dimension, left=of 21] {2d};
\node (3d) [dimension, above=of 2d] {3d};
\node (4d) [dimension, above=of 3d] {4d};
\node (5d) [dimension, above=of 4d] {5d};
\node (6d) [dimension, above=of 5d] {6d};
\node (7d) [dimension, above=of 6d] {7d};
\node (8d) [dimension, above=of 7d] {8d};
\node (9d) [dimension, above=of 8d] {9d};
\node (10d) [dimension, above=of 9d] {10d};
\end{tikzpicture}
\caption{Orbits of square-zero supercharges.}
\label{fig:superchargeorbits}
\end{figure}
%\end{landscape}

@@

\begin{theorem}\label{10d_twist_thm}
The holomorphic twist of 10d super Yang-Mills theory on a Calabi-Yau 5-fold $X_5$ is equivalent to holomorphic Chern-Simons theory on $X_5$.
\end{theorem}

@@

\subsection{Dimension 9}
The 9-dimensional $\mc N=1$ super Yang-Mills theory is obtained by dimensional reduction of $\mc N=1$ super Yang-Mills from $\RR^{10}$ to $\RR^9$.  It has BRST fields given by a ghost, a 9d gauge field $A$, a $\gg$-valued scalar field $\phi$, and a Dirac spinor field $\lambda$.

\chris{There is a single non-zero class of square zero supercharges in 9d, which are minimal (i.e. have 5d image).  They are stabilized by $\SU(4)$.  The twisted theory is only $\ZZ/2\ZZ$-graded.}

\begin{theorem}
The minimal twist of 9d super Yang-Mills theory on the product of a Calabi-Yau 4-fold $X_4$ and an oriented 1-manifold $L = \RR$ or $S^1$ is equivalent to mixed Chern-Simons theory on $X_4 \times L_\mr{dR}$.
\end{theorem}

The relevant fields for this calculation are those component fields which survived the 10d holomorphic twist of Theorem \ref{10d_twist_thm}.  These fields, in the BRST formalism, decompose as
\begin{align*}
B^{10} &= B + A \wedge \d \ol z^5 \in (\Omega^{0,2}(\CC^4; \gg) \oplus \Omega^{0,1}(\CC^4; \gg)) \otimes \Omega^0(\RR x_9) \\
A^{10}_{0,1} &= A' + \phi \d \ol z^5 \in (\Omega^{0,1}(\CC^4; \gg) \oplus \Omega^0(\CC^4; \gg)) \otimes \Omega^0(\RR x_9)
\end{align*}
along with the ghost $c$. \chris{can prove the theorem by the same argument as in 10d, or using dimensional reduction.}

@@

% \cN=1 SYM, three twists

@@

% \cN=1 SYM, three twists identical to dimension 8

@@

% \cN=(1, 1) SYM, three twists identical to dimension 8

% \cN=(1, 0) SYM with matter in a pseudo-real representation, one twist.

@@

% \cN=2 SYM, three twists
% \cN=1 SYM with matter in a pseudo-real representation, one twist.

@@
